Raft Distributed Consensus Algorithm over WebRTC (Web Real-Time Communication)

### 2015-09-06 research_class/paper.tex
Proofread and citations up through section 4.
Move WebRTC protocol standards/drafts links to bibliography sections.

Raft.js is an implementation of the Raft algorithm in JavaScript that
was created by the author of this paper. %TODO/CITE
Raft.js is designed to run in either a browser environment or within
Node.js (server-side JavaScript). Raft.js implements the Raft
algorithm as described in \cite[Consensus:~Diego]{raft_thesis:ongaro14}.

@@

The modular design of the Raft.js implementation allows it to be
easily used in different contexts. For example, the \texttt{RaftServerLocal}
class (\texttt{local.js}) implements RPC calls using plain JavaScript function
calls between different instances of the class (nodes) in the same
execution context. For example, the online Raft visualization at
\href{http://kanaka.github.io/raft.js/}{http://kanaka.github.io/raft.js/}
uses the \texttt{RaftServerLocal} class and instantiates it using
a scheduling functions that fire when the user clicks on the "Step"
button rather than due to the passage of time.

@@

\begin{enumerate}
\item The paper describes the Raft RPCs in terms of the traditional
    request/response model where requests and responses are
    automatically correlated together by a lower level of the software
    stack. For example with HTTP 1.0 a separate network session is
    established for each request/response pair (HTTP 1.0). Other
    examples including using a unique per session ID to correlate
    request and response.  WebRTC DataChannel connections are message
    based rather than request/response based. The original Raft
    definition of RPC and RPC response messages almost contain enough
    information to function correctly in an environment without
    builtin request/response correlation. Raft.js includes a small
    modification to the response RPCs for requestVote and
    appendEntries to add a 'sourceId' field.
\item The Raft paper is clear that each membership change must be
    delayed until all the previous membership change is committed
    (sequential).  It is implied that the leader node should track all
    pending membership change requests and apply them one at a time.
    However, in Raft.js, if a client requests a membership change
    while another change request is pending (uncommitted), the leader
    will reject the change request with a status of
    'PENDING\_CONFIG\_CHANGE'. This keeps the core Raft implementation
    simpler with the trade-off being that the client implementation of
    membership change requests is slightly more complex.
\end{enumerate}

@@

WebRTC is name of a collection of browser APIs and network protocols
that are currently being standardized the W3C and IETF respectively.
Collectively, these APIs and protocols work together to enable
real-time peer-to-peer video, audio and data communication between
browsers.

@@

One of the challenges with browser-to-browser communication (and
direct peer-to-peer communication in general) is that the web browser
environment or user agent (UA) is usually running behind a firewall in
a private internet subnet. This complicates direct communication in
several ways: the public Internet address of the user agent is unknown
and dynamic, inbound connections are denied by default, and outbound
connections are network address translated (NATed).

To establish a direct communication channel between browsers, WebRTC
uses mechanism that is similar to the Session Initiation Protocol
(SIP) commonly used for Voice-over-IP (VoIP) communication. This
involves a third party server known as a signaling server. Each user
agent (browser) connects to this server at a well known address in
order to establish a direct connection to other user agents. The
signaling server is also uses to communicate session control messages
(open, close, error) and to negotiate media capabilities. The signaling
server may optionally provide other services such as higher level
session management, HTTP serving of the web application, address book
service, client presence/availability, etc.

@@

The WebRTC browser APIs enable web applications written in JavaScript
to establish browser-to-browser network connectivity in order to
stream real-time video, audio and data communication. These APIs are
currently in the process of being standardized by the W3C organization
(http://www.w3.org/TR/webrtc/) % TODO/CITE

There are three primary WebRTC API definitions:

\begin{enumerate}
\item \href{http://www.w3.org/TR/webrtc/\#rtcpeerconnection-interface}{RTCPeerConnection}: The RTCPeerConnection API represents a direct connection between two browsers. Each RTCPeerConnection object has an associated Interactive Connectivity Establishment (ICE) agent that is used to establish network connectivity through firewalls and NAT services.

\item \href{http://www.w3.org/TR/webrtc/\#media-stream-api-extensions-for-network-use}{MediaStream (aka getUserMedia}: The MediaStream API represents a stream of audio or video data.  MediaStreams can easily be sent and received over RTCPeerConnections. The MediaStream API definition provides a mechanism that allows JavaScript to enumerate the native MediaStreams that are provided by the browser such as a local web camera or a live video stream of the desktop (for desktop sharing).  Although support for MediaStreams was the original impetus for the creation of the WebRTC APIs and protocols, the Raft over WebRTC implementation does not make use of the MediaStream API.

\item \href{http://www.w3.org/TR/webrtc/\#rtcdatachannel}{RTCDataChannel}: The RTCDataChannel API provides a mechanism for sending and receiving generic data. A single RTCPeerConnection can contain multiple RTCDataChannels. The RTCDataChannel API is modeled after the WebSocket API, however, unlike the WebSocket API which is reliable and guaranteed order transport (like TCP), each RTCDataChannel can be configured with different reliability and ordering settings. For example, by relaxing the reliability and ordering constraints on a RTCDataChannel, the average latency and jitter per message can be decreased even though some messages may be dropped or arrive out of order. The Raft protocol is specifically designed to support dropped or out-of-order messages so the transport options available with RTCDataChannel can be used to gain extra efficiency.
\end{enumerate}

@@

There is a large suite of protocols that are required for a working
WebRTC system. The Internet Engineering Task Force (IETF) organization
is responsible for specifying and/or standardizing (where necessary)
the protocols that are part of WebRTC. In many cases an existing
protocol is applicable and is referenced or extended as part of the
WebRTC suite.

Describing all the protocols that make up the WebRTC suite is beyond
the scope of the this document. However, here is a (incomplete) list
of WebRTC protocols drafts and related protocols that are
part of WebRTC:

\begin{enumerate}
\item General:
    \begin{enumerate}
    \item \href{https://tools.ietf.org/html/draft-ietf-rtcweb-overview-13}{WebRTC: Overview}
    \item \href{https://tools.ietf.org/html/draft-ietf-rtcweb-security-arch-11}{WebRTC: Security Architecture}
    \item \href{https://tools.ietf.org/html/draft-ietf-rtcweb-security-08}{WebRTC: Security Considerations}
    \end{enumerate}
\item Data transport:
    \begin{enumerate}
    \item \href{https://tools.ietf.org/html/draft-ietf-rtcweb-transports-08}{WebRTC: Data transport overview}
    \item \href{https://tools.ietf.org/html/draft-ietf-tsvwg-rtcweb-qos-03}{WebRTC: DSCP and other packet markings for RTCWeb QoS}
    \item \href{https://tools.ietf.org/html/draft-ietf-tsvwg-sctp-dtls-encaps-09}{DTLS Encapsulation of SCTP Packets}
    \item \href{https://tools.ietf.org/html/draft-ietf-mmusic-sctp-sdp-14}{Stream Control Transmission Protocol (SCTP)-Based Media Transport in the Session Description Protocol (SDP)}
    \item \href{https://tools.ietf.org/html/draft-ietf-tsvwg-sctp-ndata-02}{Stream Schedulers and a New Data Chunk for the Stream Control Transmission Protocol}
    \item \href{https://tools.ietf.org/html/draft-ietf-rtcweb-rtp-usage-23}{WebRTC: Media Transport and Use of RTP}
    \item \href{https://tools.ietf.org/html/draft-ietf-rtcweb-data-channel-13}{WebRTC: Data Channels}
    \item \href{https://tools.ietf.org/html/draft-ietf-rtcweb-data-protocol-09}{WebRTC: Data Channel Establishment Protocol}
    \item \href{https://tools.ietf.org/html/draft-ietf-rtcweb-alpn-01}{WebRTC: Application Layer Protocol Negotiation for Web Real-Time Communications (WebRTC)}
    \item \href{https://tools.ietf.org/html/rfc5245}{RFC5245: Interactive Connectivity Establishment (ICE)}
    \item \href{https://tools.ietf.org/html/rfc5128}{RFC5128: Peer-to-Peer (P2P) Communication across Network Address Translators (NATs)}
    \item \href{https://tools.ietf.org/html/rfc5389}{RFC5389: Session Traversal Utilities for NAT (STUN)}
    \item \href{https://tools.ietf.org/html/rfc3489}{RFC3489: STUN - Simple Traversal of User Datagram Protocol (UDP) Through Network Address Translators (NATs)}
    \item \href{https://tools.ietf.org/html/rfc5766}{RFC5766: Traversal Using Relays around NAT (TURN)}
    \item \href{https://tools.ietf.org/html/rfc6156}{RFC6156: Traversal Using Relays around NAT (TURN) Extension for IPv6}
    \item \href{https://tools.ietf.org/html/rfc6544}{RFC6544: TCP Candidates with Interactive Connectivity  Establishment (ICE)}
    \item \href{https://tools.ietf.org/html/RFC4571}{RFC4571: Framing Real-time Transport Protocol (RTP) and RTP Control Protocol (RTCP) Packets over Connection-Oriented Transport}
    \item \href{https://tools.ietf.org/html/rfc5764}{RFC5764: Datagram Transport Layer Security (DTLS) Extension to Establish Keys for the Secure Real-time Transport Protocol (SRTP)}
    \end{enumerate}

\item Data framing and security
    \begin{enumerate}
    \item \href{https://tools.ietf.org/html/rfc3550}{RFC3550: Real-time Transport Protocol (RTP)}
    \item \href{https://tools.ietf.org/html/rfc3711}{RFC3711: Secure Real-time Transport Protocol (SRTP)}
    \item \href{https://tools.ietf.org/html/draft-ietf-rtcweb-rtp-usage-23}{WebRTC: Media Transport and Use of RTP}
    \item \href{https://tools.ietf.org/html/draft-ietf-rtcweb-data-channel-13}{WebRTC: Data Channels}
    \item \href{https://tools.ietf.org/html/draft-ietf-rtcweb-data-protocol-09}{WebRTC: Data Channel Establishment Protocol}
    \end{enumerate}
\item Data formats (audio)
    \begin{enumerate}
    \item \href{https://tools.ietf.org/html/draft-cbran-rtcweb-codec-02}{WebRTC: WebRTC Codec and Media Processing Requirements}
    \item \href{https://tools.ietf.org/html/draft-ietf-rtcweb-audio-07}{WebRTC: Audio Codec and Processing Requirements}
    \item \href{https://tools.ietf.org/html/rfc6716}{RFC6716: Opus Audio Codec}
    \item \href{https://tools.ietf.org/html/draft-ietf-payload-rtp-opus-11}{RTP Payload Format for Opus Speech and Audio Codec}
    \item \href{https://tools.ietf.org/html/rfc3551}{RFC3551: RTP Profile for Audio and Video Conference}
    \item \href{https://tools.ietf.org/html/rfc4733}{RFC4733: RTP Payload for DTMF Digits, Telephony Tones, and Telephony Signals}
    \item \href{https://tools.ietf.org/html/draft-ietf-rtcweb-audio-codecs-for-interop-01}{WebRTC: Additional WebRTC audio codecs for interoperability with legacy networks}
    \item \href{https://tools.ietf.org/html/draft-ietf-rtcweb-video-05}{WebRTC: Video Processing and Codec Requirements}
    \item \href{https://tools.ietf.org/html/rfc6386}{RFC6386: VP8 Data Format and Decoding Guide}
    \item \href{http://www.itu.int/rec/T-REC-H.264}{ITU H.264: Advanced video coding for generic audiovisual services}
    \item \href{https://tools.ietf.org/html/draft-ietf-payload-vp8-15}{RTP Payload Format for VP8 Video}
    \item \href{https://tools.ietf.org/html/rfc6236}{RFC6236: Negotiation of Generic Image Attributes in the Session Description Protocol (SDP)}
    \end{enumerate}

\item Connection management
    \begin{enumerate}
    \item \href{https://tools.ietf.org/html/rfc3264}{RFC3264: An Offer/Answer Model with the Session Description Protocol (SDP)}
    \item \href{https://tools.ietf.org/html/rfc2327}{RFC2327: SDP: Session Description Protocol}
    \item \href{https://tools.ietf.org/html/draft-ietf-rtcweb-jsep-09}{WebRTC: JavaScript Session Establishment Protocol (JSEP)}
    \item \href{https://tools.ietf.org/html/rfc5245}{RFC5245: Interactive Connectivity Establishment (ICE)}
    \item \href{https://tools.ietf.org/html/draft-ietf-mmusic-trickle-ice-02}{RFC5763: Trickle ICE: Incremental Provisioning of Candidates for the Interactive Connectivity Establishment (ICE) Protocol}
    \end{enumerate}
\end{enumerate}

Note: the signaling transport itself is not defined as part of WebRTC.
This is up to the application designer.

@@

The JavaScript interface use for establishing the initial connection
(signaling) in the WebRTC 1.0 standard is somewhat complicated.
A competing standard called Object Real-time Communication (ORTC) is
working to define a simpler and more modular JavaScript API for WebRTC
signaling. However, at the time of this work, the ORTC interface was
not yet widely supported and still in a state of flux.  The use of
PeerJS provides a suitable abstraction in the meantime (and will
likely be modified to support ORTC).

@@

The PeerJS project provides a simple WebRTC signaling server called
PeerServer. This server uses HTTP and WebSockets transport protocols
to perform WebRTC signaling on behalf of browser clients. The
PeerServer server is also extensible so that more advanced services
can be built with it. The PeerJS project includes an extension to
PeerServer called ExpressPeerServer that combines a PeerJS signaling
server with the Node.js based Express web application framework.
% (TODO/CITE)

@@

The PeerJS client library provides an simple abstraction over the
native browser WebRTC APIs. The WebRTC API standards are not yet
finalized and so different browsers and browser releases may support
different versions of the WebRTC draft APIs. The PeerJS client library
abstracts over these differences and provides a common interface so
that the application developer does not have to deal directly with
browser differences.

The PeerJS client library also provides a default signaling mechanism
that is designed to operate with a PeerJS signaling server. This is
particularly helpful because much of the WebRTC signaling transport
and protocol is not defined as part of the WebRTC standardization
effort. The PeerJS organization provides a cloud-hosted version of
a PeerJS compatible signaling server, however an application developer
can also run their own PeerJS signaling service using the PeerServer
server described above.

@@

% TODO: references

@@

\printbibliography
%\bibliographystyle{plain}
%\bibliography{references/raft,references/other}

>>>>

Raft.js is an implementation of the Raft algorithm in JavaScript that
was created by the author of this paper \cite{raft.js}.  Raft.js is
designed to run in either a browser environment or within Node.js
(server-side JavaScript). Raft.js implements the Raft algorithm as
described in \cite[Consensus:~Diego]{raft_thesis:ongaro14}.

@@

The modular design of the Raft.js implementation allows it to be
easily used in different contexts. For example, the \texttt{RaftServerLocal}
class (\texttt{local.js}) implements RPC calls using plain JavaScript function
calls between different instances of the class (nodes) in the same
execution context. For example, the online Raft visualization at
\href{http://kanaka.github.io/raft.js/}{http://kanaka.github.io/raft.js/}
\cite{raft.js:visualization} uses the \texttt{RaftServerLocal} class
and instantiates it using a scheduling function that executes one
scheduled event each time the user clicks on the "Step" button rather
than due to the passage of time.

@@

\begin{enumerate}
\item The paper describes the Raft RPCs in terms of synchronous stream
    based request/response model where requests and responses are
    automatically correlated together by a lower level of the software
    stack. For example with HTTP 1.0 \cite{http:rfc1945} client
    requests are followed by a server response on any given TCP
    stream. Most remote procedure call mechanims also use
    a synchronous request/response model. %TODO/CITE
    WebRTC DataChannel connections are message based rather than
    request/response stream based. %TODO/CITE
    The original Raft definition of RPC request and response messages
    almost contain enough information to function correctly in an
    environment without builtin request/response correlation such as
    UDP or SCTP when used with reliable transport disabled. %TODO/CITE
    Raft.js includes a small modification to the response RPCs for
    requestVote and appendEntries to add a 'sourceId' field that
    enables the protocol to function with message based transports.
\item The Raft paper is clear that each membership change must be
    delayed until all the previous membership change is committed
    (sequential) \cite[Section~4.1]{raft_thesis:ongaro14}. It is
    implied that the leader node should track all pending membership
    change requests and apply them one at a time.  However, in
    Raft.js, if a client requests a membership change while another
    change request is pending (uncommitted), the leader will reject
    the change request with a status of 'PENDING\_CONFIG\_CHANGE'.
    This keeps the core Raft implementation simpler with the trade-off
    being that the client implementation of membership change requests
    is slightly more complex due to retry logic.
\end{enumerate}

@@

WebRTC is a collection of browser APIs \cite{webrtc:feb2015} and
network protocols \cite{draft-rtcweb-overview} that are currently
being standardized the W3C and IETF respectively. Collectively these
APIs and protocols enable real-time peer-to-peer video, audio and data
communication between browsers.

@@

One of the challenges with browser-to-browser communication (and
direct peer-to-peer communication in general) is that the web browser
environment or user agent (UA) is usually running behind a firewall in
a private internet subnet. This complicates direct communication in
several ways: the public Internet address of the user agent is unknown
and dynamic, inbound connections are denied by default, and outbound
connections are network address translated (NATed)
\cite[Section~3.4]{draft-rtcweb-transports}.

To establish a direct communication channel between browsers, WebRTC
uses mechanism called Interactive Connectivity Establishment (ICE)
that is similar to the Session Initiation Protocol (SIP) commonly used
for Voice-over-IP (VoIP) communication \cite{RFC5245:ice}. This
involves a third party server known as a signaling server. Each user
agent (browser) connects to this server at a well known address in
order to establish a direct connection to other user agents. The
signaling server is also uses to communicate session control messages
(open, close, error) and to negotiate media capabilities. %TODO/CITE
The signaling server may optionally provide other services such as
higher level session management, HTTP serving of the web application,
address book service, client presence/availability, etc. %TODO/CITE

@@

The WebRTC browser APIs enable web applications written in JavaScript
to establish browser-to-browser network connectivity in order to
perform real-time video, audio and data communication. These APIs are
currently in the process of being standardized by the \emph{Web
Real-Time Communications Working Group} of the World Wide Web
Consortium (W3C) \cite{webrtc:wg}.

There are three primary WebRTC interfaces:

\begin{enumerate}
\item \emph{RTCPeerConnection} \cite{webrtc:rtcpeerconnection:feb2015}:
    The RTCPeerConnection API represents a direct connection between
    two browsers. Each RTCPeerConnection object has an associated
    Interactive Connectivity Establishment (ICE) agent that is used to
    establish network connectivity through firewalls and NAT services.

\item \emph{MediaStream~(aka~getUserMedia)} \cite{webrtc:media-stream:feb2015}:
    The MediaStream API represents a stream of audio or video data.
    MediaStream data can easily be sent and received over
    RTCPeerConnections. The MediaStream API definition provides
    a mechanism that allows JavaScript to enumerate the native
    MediaStreams that are provided by the browser such as a local web
    camera or a live video stream of the desktop (for desktop
    sharing).  Although support for MediaStreams was the original
    impetus for the creation of the WebRTC APIs and protocols, the
    Raft over WebRTC implementation does not make use of the
    MediaStream API.

\item
    \emph{RTCDataChannel} \cite{webrtc:datachannel:feb2015}:
    The RTCDataChannel API provides a mechanism for sending and
    receiving generic data between User Agents (browsers). A single
    RTCPeerConnection can contain multiple RTCDataChannels. The
    RTCDataChannel API is modeled after the WebSocket API, however,
    unlike the WebSocket API which is reliable and guaranteed order
    transport (like TCP), each RTCDataChannel can be configured with
    different reliability and ordering settings. For example, by
    relaxing the reliability and ordering constraints on
    a RTCDataChannel, the average latency and jitter per message can
    be decreased even though some messages may be dropped or arrive
    out of order. The Raft protocol is specifically designed to
    support dropped or out-of-order messages so the transport options
    available with RTCDataChannel can be used to gain extra
    efficiency.
    %TODO/CITE: more of them above
\end{enumerate}

@@

There is a large suite of protocols that are required for a working
WebRTC system. The Internet Engineering Task Force (IETF) organization
is responsible for specifying and/or standardizing (where necessary)
the protocols that are part of WebRTC. In many cases an existing
protocol is applicable and is referenced or extended as part of the
WebRTC suite. %TODO/CITE

The protocols that make up the WebRTC suite are categorized into
five general functionality groups:

\begin{enumerate}
    \item data transport
    \item data framing and security
    \item connection management
    \item data formats
    \item presentation and control
    \item and local system support functions
\end{enumerate}

The last three functionality groups focus on interactive audio and video
applications and are less relevant to Raft over WebRTC. The WebRTC
section of the bibliography %TODO: reference link
has a (incomplete) list of WebRTC specific protocols drafts and other
related protocol standards for the first three functionality groups
(data transport, data framing and security, and connection
management).

The signaling transport itself is not defined as part of WebRTC.
This is up to the application designer. The JavaScript interface used
for establishing the initial connection (signaling) in the WebRTC 1.0
standard is somewhat complicated. A competing standard called Object
Real-time Communication (ORTC) is working to define a simpler and more
modular JavaScript API for WebRTC signaling \cite{ortc2014}. However,
at the time of this paper, the ORTC interface was not yet widely
supported and still in a state of flux. The use of PeerJS provides an
abstraction that is likely to transparently support ORTC in the future.

@@

@@

The PeerJS project provides a simple WebRTC signaling server called
PeerServer. This server uses HTTP and WebSockets transport protocols
to perform WebRTC signaling on behalf of browser clients. The
PeerServer server is also extensible so that more advanced services
can be built with it. The PeerJS project includes an extension to
PeerServer called ExpressPeerServer that combines a PeerJS signaling
server with the popular Node.js ExpressJS web application framework.
% (TODO/CITE)

@@

The PeerJS client library provides an simple abstraction over the
native browser WebRTC APIs. The WebRTC API standards are not yet
finalized and so different browsers and browser releases may support
different versions of the WebRTC draft APIs. %TODO/CITE
The PeerJS client library abstracts over these differences and
provides a common interface so that the application developer does not
have to deal directly with browser differences.

The PeerJS client library also provides a default signaling mechanism
that is designed to operate with a PeerJS signaling server. This is
particularly helpful because much of the WebRTC signaling transport
and protocol is not defined as part of the WebRTC standardization
effort. %TODO/CITE
The PeerJS organization provides a cloud-hosted version of a PeerJS
compatible signaling server, however an application developer can also
run their own signaling service using PeerJS PeerServer.

@@

@@

\printbibliography[title={General references},notkeyword=rtc-general,notkeyword=rtc-transport,notkeyword=rtc-framing]

\nocite{draft-rtcweb-overview}
\nocite{draft-rtcweb-security-arch}
\nocite{draft-rtcweb-security}
\printbibliography[title={WebRTC general references},keyword=rtc-general]

\nocite{draft-rtcweb-transports}
\nocite{draft-rtcweb-qos}
\nocite{RFC4960:sctp}
\nocite{RFC3758:sctp-reliability}
\nocite{draft-sctp-dtls-encaps}
\nocite{draft-mmusic-sctp-sdp}
\nocite{draft-sctp-ndata}
\nocite{draft-rtcweb-rtp-usage}
\nocite{draft-rtcweb-data-channel}
\nocite{draft-rtcweb-data-protocol}
\nocite{draft-rtcweb-alpn}
\nocite{RFC5245:ice}
\nocite{RFC5128:p2p-nat}
\nocite{RFC5389:stun}
\nocite{RFC3489:stun-udp}
\nocite{RFC5766:turn}
\nocite{RFC6156:turn-ipv6}
\nocite{RFC6544:tcp-ice}
\nocite{RFC4571:rtp-rtcp}
\nocite{RFC5764:dtls-srtp}
\printbibliography[title={WebRTC data transport},keyword=rtc-transport]

\nocite{RFC3550:rtp}
\nocite{RFC3711:srtp}
%\nocite{draft-rtcweb-rtp-usage}
%\nocite{draft-rtcweb-data-channel}
%\nocite{draft-rtcweb-data-protocol}
\printbibliography[title={WebRTC framing and security},keyword=rtc-framing]

\nocite{RFC2327:sdp}
\nocite{RFC3264:sdp-offer-answer}
\nocite{draft-rtcweb-jsep}
%\nocite{RFC5245:ice}
\nocite{draft-mmusic-trickle-ice}
\nocite{RFC5763:srtp-using-dtls}
\printbibliography[title={WebRTC connection management},keyword=rtc-connection]

%%%

%\begin{enumerate}
%\item Data formats (audio)
%    \begin{enumerate}
%    \item \href{https://tools.ietf.org/html/draft-cbran-rtcweb-codec-02}{WebRTC: WebRTC Codec and Media Processing Requirements}
%    \item \href{https://tools.ietf.org/html/draft-ietf-rtcweb-audio-07}{WebRTC: Audio Codec and Processing Requirements}
%    \item \href{https://tools.ietf.org/html/rfc6716}{RFC6716: Opus Audio Codec}
%    \item \href{https://tools.ietf.org/html/draft-ietf-payload-rtp-opus-11}{RTP Payload Format for Opus Speech and Audio Codec}
%    \item \href{https://tools.ietf.org/html/rfc3551}{RFC3551: RTP Profile for Audio and Video Conference}
%    \item \href{https://tools.ietf.org/html/rfc4733}{RFC4733: RTP Payload for DTMF Digits, Telephony Tones, and Telephony Signals}
%    \item \href{https://tools.ietf.org/html/draft-ietf-rtcweb-audio-codecs-for-interop-01}{WebRTC: Additional WebRTC audio codecs for interoperability with legacy networks}
%    \item \href{https://tools.ietf.org/html/draft-ietf-rtcweb-video-05}{WebRTC: Video Processing and Codec Requirements}
%    \item \href{https://tools.ietf.org/html/rfc6386}{RFC6386: VP8 Data Format and Decoding Guide}
%    \item \href{http://www.itu.int/rec/T-REC-H.264}{ITU H.264: Advanced video coding for generic audiovisual services}
%    \item \href{https://tools.ietf.org/html/draft-ietf-payload-vp8-15}{RTP Payload Format for VP8 Video}
%    \item \href{https://tools.ietf.org/html/rfc6236}{RFC6236: Negotiation of Generic Image Attributes in the Session Description Protocol (SDP)}
%    \end{enumerate}
%\end{enumerate}
